manuscript_outline

### 2025-07-17 docs/manuscript/paper.Rmd
fix figure formatting

p2 <- ascaphus_ef |>
  ggplot() +
  geom_point(aes(x = temp, y = ef)) +
  geom_line(aes(x = temp, y = ef)) +
  geom_line(data = data_1, aes(x = t, y = e), linetype = "dashed") +
  # geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value") +
  theme_classic()

@@

# model_data |>
#   ggplot() +
#   geom_density_ridges(aes(y = as.factor(year), x = days , fill = Mountain)) +
#   theme_classic() +
#   theme(legend.position = "none")
# 
# model_data |>
#   ggplot(aes(x = year, y = days , color= Mountain, group = comid)) +
#   geom_point() +
#   #geom_line() +
#   geom_smooth(method = "lm", se = FALSE) +
#   labs(x= "Year", y = "Hatch Date") +
#   theme_classic() +
#   theme(legend.position = c(0.8, 0.75))

@@

p.01 <- means_all |> 
  ggplot(aes(year, Mean, ymin = CI_low, ymax = CI_high)) +
  geom_ribbon(alpha = 0.05, color = NA) +
  geom_line(size = 1.1)  +
  lims(y = c(20,27)) +
  labs(x = "Year", y = "Mean of Days to Hatch") +
  theme_classic()

@@

p.02 <- means |> 
  ggplot(
    aes(
      x = year, y = Mean,
      ymin = CI_low, ymax = CI_high,
      group = comid,
      fill = Mountain,
      color = Mountain, 
      # linetype = comid
    )
  ) +
  geom_line(size = 1.1) +
  geom_ribbon(alpha = 0.05, color = NA) +
  labs(x = "Year", y = "Mean of Days to Hatch") +
  theme_classic()

@@

# estimate_means(mod, c("year", "comid")) |>
#   plot() +
#   #geom_point(data = pred_hatch, aes(x = year, y = days, color = Mountain), size = 0.5 , alpha = 0.25) +
#   labs(x = "Year", y = "Mean of Days to Hatch") +
#   theme_classic()
```

@@

p2.1.a <- ggplot() +
  geom_point(data = temperature_data_cold, aes(x = dates, y = temperatures)) +
  geom_line(data = temperature_data_cold, aes(x = dates, y = temperatures)) +
  geom_rect(data = froggy_hatch_cold, aes(xmin = start, xmax = stop, ymax = index - .15, ymin = index - .5, fill = species)) +
  geom_label(data = froggy_hatch_cold, aes(x = start + (stop - start) / 1.45, y = (index - 0.325), label = days_to_develop)) +
  labs(x = "Date", y = "Temperature (°C)") +
  scale_fill_manual(values = c("darkolivegreen4", "deepskyblue4", "grey23", "purple4"), name = "Species") +
  theme_classic() +
  theme(legend.position = c(0.75, 0.25))

@@

p2.1.b <- ggplot() +
  geom_point(data = temperature_data_warm, aes(x = dates, y = temperatures)) +
  geom_line(data = temperature_data_warm, aes(x = dates, y = temperatures)) +
  geom_rect(data = froggy_hatch_warm, aes(xmin = start, xmax = stop, ymax = index - .15, ymin = index - .5, fill = species)) +
  geom_label(data = froggy_hatch_warm, aes(x = start + (stop - start) / 1.45, y = (index - 0.325), label = days_to_develop)) +
  labs(x = "Date", y = "Temperature (°C)") +
  scale_fill_manual(values = c("darkolivegreen4", "deepskyblue4", "grey23", "purple4"), name = "Species") +
  theme_classic() +
  theme(legend.position = "none")

@@

p2.2 <- ef_vals |>
  tibble() |>
  ggplot(aes(x = temperature, y = effective_value, color = frog_species)) +
  geom_line() +
  geom_point() +
  geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value") +
  scale_color_manual(values = c("darkolivegreen4", "deepskyblue4", "grey23", "purple4"), name = "Species") +
  theme_classic() +
  theme(legend.position = "none")

@@

fig4 <- ef_vals_pops |>
  tibble() |>
  ggplot(aes(x = temperature, y = effective_value, color = beetle_pops)) +
  geom_line() +
  geom_point() +
  # geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value", title = "Figure 4") +
  scale_color_brewer(palette = "Dark2", name = "Beetle Populations") +
  theme_classic() +
  theme(legend.position = c(0.25, 0.75))

@@

```{r fig.width=8, fig.height=8, fig.align='center', fig.cap=""}
fig3
```

>>>>

p2 <- ascaphus_ef |>
  ggplot() +
  geom_point(aes(x = temp, y = ef)) +
  geom_line(aes(x = temp, y = ef)) +
  geom_line(data = data_1, aes(x = t, y = e), linetype = "dashed") +
  # geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value") +
  theme_classic(base_size = 16)

@@

# model_data |>
#   ggplot() +
#   geom_density_ridges(aes(y = as.factor(year), x = days , fill = Mountain)) +
#   theme_classic(base_size = 16) +
#   theme(legend.position = "none")
# 
# model_data |>
#   ggplot(aes(x = year, y = days , color= Mountain, group = comid)) +
#   geom_point() +
#   #geom_line() +
#   geom_smooth(method = "lm", se = FALSE) +
#   labs(x= "Year", y = "Hatch Date") +
#   theme_classic(base_size = 16) +
#   theme(legend.position = c(0.8, 0.75))

@@

p.01 <- means_all |> 
  ggplot(aes(year, Mean, ymin = CI_low, ymax = CI_high)) +
  geom_ribbon(alpha = 0.05, color = NA) +
  geom_line(size = 1.1)  +
  lims(y = c(20,27)) +
  labs(x = "Year", y = "Mean of Days to Hatch") +
  theme_classic(base_size = 16)

@@

p.02 <- means |> 
  ggplot(
    aes(
      x = year, y = Mean,
      ymin = CI_low, ymax = CI_high,
      group = comid,
      fill = Mountain,
      color = Mountain, 
      # linetype = comid
    )
  ) +
  geom_line(size = 1.1) +
  geom_ribbon(alpha = 0.05, color = NA) +
  labs(x = "Year", y = "Mean of Days to Hatch") +
  theme_classic(base_size = 16)

@@

# estimate_means(mod, c("year", "comid")) |>
#   plot() +
#   #geom_point(data = pred_hatch, aes(x = year, y = days, color = Mountain), size = 0.5 , alpha = 0.25) +
#   labs(x = "Year", y = "Mean of Days to Hatch") +
#   theme_classic(base_size = 16)
```

@@

p2.1.a <- ggplot() +
  geom_point(data = temperature_data_cold, aes(x = dates, y = temperatures)) +
  geom_line(data = temperature_data_cold, aes(x = dates, y = temperatures)) +
  geom_rect(data = froggy_hatch_cold, aes(xmin = start, xmax = stop, ymax = index - .15, ymin = index - .5, fill = species)) +
  geom_label(data = froggy_hatch_cold, aes(x = start + (stop - start) / 1.45, y = (index - 0.325), label = days_to_develop)) +
  labs(x = "Date", y = "Temperature (°C)") +
  scale_fill_manual(values = c("darkolivegreen4", "deepskyblue4", "grey23", "purple4"), name = "Species") +
  theme_classic(base_size = 16) +
  theme(legend.position = c(0.75, 0.25))

@@

p2.1.b <- ggplot() +
  geom_point(data = temperature_data_warm, aes(x = dates, y = temperatures)) +
  geom_line(data = temperature_data_warm, aes(x = dates, y = temperatures)) +
  geom_rect(data = froggy_hatch_warm, aes(xmin = start, xmax = stop, ymax = index - .15, ymin = index - .5, fill = species)) +
  geom_label(data = froggy_hatch_warm, aes(x = start + (stop - start) / 1.45, y = (index - 0.325), label = days_to_develop)) +
  labs(x = "Date", y = "Temperature (°C)") +
  scale_fill_manual(values = c("darkolivegreen4", "deepskyblue4", "grey23", "purple4"), name = "Species") +
  theme_classic(base_size = 16) +
  theme(legend.position = "none")

@@

p2.2 <- ef_vals |>
  tibble() |>
  ggplot(aes(x = temperature, y = effective_value, color = frog_species)) +
  geom_line() +
  geom_point() +
  geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value") +
  scale_color_manual(values = c("darkolivegreen4", "deepskyblue4", "grey23", "purple4"), name = "Species") +
  theme_classic(base_size = 16) +
  theme(legend.position = "none")

@@

fig4 <- ef_vals_pops |>
  tibble() |>
  ggplot(aes(x = temperature, y = effective_value, color = beetle_pops)) +
  geom_line() +
  geom_point() +
  # geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily Average Temperature (°C)", y = "Effective Value", title = "Figure 4") +
  scale_color_brewer(palette = "Dark2", name = "Beetle Populations") +
  theme_classic(base_size = 16) +
  theme(legend.position = c(0.25, 0.75))

@@

```{r fig.width=8, fig.height=10, fig.align='center', fig.cap=""}
fig3
```
